% Page Layout
\setuppapersize[letter]
\setuplayout[grid=yes,backspace=1in,margin=0in,rightedge=0in,rightmargin=0in,topspace=1in,header=0in,footer=0in]

% Fonts
\definefontfamily [mainface] [rm] [Minion Pro]
\definefontfamily [headerface] [rm] [Myriad Pro]
\setupbodyfont[mainface]
\setuphead[section][style=\headerface]

\defineparagraphs[TwoColumns][n=2]
\setupparagraphs[TwoColumns][1][tolerance=verytolerant,width=0.61996\textwidth]

\definecolumnset[GoldenColumns][n=2]
\setupcolumnset[GoldenColumns][width=0.61996\textwidth]

\setupinteraction[state=start,color=green]
\showgrid
\showframe

\useURL[author-email][mailto:joe.schafer@delta46.us][][joe.schafer@delta46.us]
\useURL[author-linkedin][http://linkedin.com/in/jschaf][][linkedin.com/in/jschaf]
\useURL[author-github][http://github.com/jschaf][][github.com/jschaf]
\useURL[author-blog][http://blog.d46.us][][blog.d46.us]
\useURL[eslint-closure][https://github.com/google/eslint-closure][][library]

\define[1]\Action{{\bf #1}}

\define[3]\WorkHeading{%
\starttable[|lp(.3\textwidth)s0|lp(.4\textwidth)s0|rp(.3\textwidth)s0|]
\NC #1  \NC #2 \NC #3 \NC\NR
\stoptable%
}


\starttext
\startcolumnset [GoldenColumns]
% \startTwoColumns

Joe Schafer

\startsection[title={Work Experience}]

\WorkHeading{Google}{Software Engineer}{2016-present}
\startitemize
\item \Action{Released} an open source \from[eslint-closure] to check the style
  of Google Closure JavaScript code.
\item \Action{Split} a 4\high{GB} monolithic binary into 3 microservices.
\item \Action{Developed} a project management application that integrates with Gmail
  through JavaScript, Python and Java.
\item \Action{Reduced} application testing time 20-fold by implementing hot-reload of JavaScript.
\stopitemize

\WorkHeading{U.S. Army}{Infantry Instructor}{2014-16}
\startitemize
\item \Action{Influenced} 5 levels of executives to transition the Infantry
  training course to a committee design resulting in every subsequent class
  achieving record high performance.
\item \Action{Taught} and \Action{mentored} 120 Infantry lieutenants to lead a
  platoon in battle and plan decisive operations.

\stopitemize

\WorkHeading{U.S. Army}{Infantry Officer}{2010-14}
\startitemize
\item \Action{Planned} all logistics operations for an 815-man Airborne Infantry
  Battalion capable of worldwide deployment in 96 hours.

\item \Action{Planned} and \Action{led} 25 combat missions in Afghanistan
  through 6 enemy ambushes and Improvised Explosive Device (IED) attacks.
\stopitemize
\stopsection


\column
\from[author-email]

\from[author-linkedin]

\from[author-github]

\from[author-blog]

Pellentesque dapibus suscipit ligula.  Donec posuere augue in quam.  Etiam vel
tortor sodales tellus ultricies commodo.  Suspendisse potenti.  Aenean in sem ac
leo mollis blandit.  Donec neque quam, dignissim in, mollis nec, sagittis eu,
wisi.  Phasellus lacus.  Etiam laoreet quam sed arcu.  Phasellus at dui in
ligula mollis ultricies.  Integer placerat tristique nisl.  Praesent augue.
Fusce commodo.  Vestibulum convallis, lorem a tempus semper, dui dui euismod
elit, vitae placerat urna tortor vitae lacus.  Nullam libero mauris, consequat
quis, varius et, dictum id, arcu.  Mauris mollis tincidunt felis.  Aliquam
feugiat tellus ut neque.  Nulla facilisis, risus a rhoncus fermentum, tellus
tellus lacinia purus, et dictum nunc justo sit amet elit.

\stopcolumnset
% \stopTwoColumns


\stoptext