% Page Layout
\setuppapersize[letter]
\setuplayout[grid=yes,width=6.5in,header=0pt]

% Fonts

% \definefontfamily [mainface] [rm] [Minion Pro]
% \definefontfamily [headerface] [rm] [Myriad Pro]

% default line=2.8ex
\newdimen\Baseline
\Baseline=14pt
\newdimen\SmallBaseline
\SmallBaseline=0.806\Baseline
\setupinterlinespace[line=\Baseline]

\definefontfeature[default][default]
                  [protrusion=quality, expansion=quality, onum=yes]
\setupalign[hz,hanging]


\definefontalternative[se]
\definefontalternative[liit]
\definefontalternative[li]
\definefontalternative[me]
\definefontalternative[meit]
\definefontalternative[seit]
\definefontalternative[bl]
\definefontalternative[blit]


\usetypescript[type-adobe]
\usetypescript[type-minionpro]
\usetypescript[type-myriadpro]
\starttypescript [myfont]
   \definetypeface [myfont] [rm] [serif] [minionpro] [regular]
   \definetypeface [myfont] [ss] [sans]  [myriadpro] [regular]
   \definetypeface [myfont] [tt] [mono]  [cursor]    [default] [rscale=1.163]
   \definetypeface [myfont] [mm] [math]  [palatino]  [default] [rscale=1.050]
\stoptypescript
\setupbodyfont[myfont,11pt]

% Hyphenation
\hyphenation{Goo-gle Type-Script Git-Hub}

% Columns
\define\GoldenRatio{0.61996}
\newdimen\ColumnGutter
\ColumnGutter=1cm
\defineparagraphs[GoldenColumns][n=2]
\setupparagraphs[GoldenColumns][1][width=\dimexpr\GoldenRatio\textwidth - 0.5\ColumnGutter\relax]
\setupparagraphs[GoldenColumns][2][distance=\ColumnGutter]

% Content
\define[1]\Name{\blank[12pt]{\tfd #1}}
\define[1]\Heading{\blank[0.6\Baseline]\color[HeadingColor]{\ssa #1}\par\blank[halfline]}
\define\CompanyLength{2.7cm}
\define[3]\WorkHeading{%
  \dontleavehmode\hbox to \CompanyLength{#1\hfil} #2 \hfill #3}
\define[2]\EducationHeading{{\se #1}\hfill #2\par}

\define[2]\OpenSourceProject{%
  {\tf #1}\par%
  \startbaselinecorrection
  \setupinterlinespace[line=\SmallBaseline]
  \startalignment[flushleft] {\tfx #2} \stopalignment
  \stopbaselinecorrection
}

\define[1]\Contact{{\tfx #1\par}}
\define[2]\LanguageProficiency{%
  \startalignment[flushleft] \tfx {\se #1}:  #2 \stopalignment
}
\define[1]\Hobby{%
  \startalignment[flushleft]{\tfx #1}\stopalignment}

% Colors
\definecolor[HeadingColor][0.6(red,black)]
\definecolor[UrlColor][0.6(blue,black)]

\setupitemize[each][packed,inmargin][symbol=nosymbol]
\setupinteraction[state=start,color=UrlColor,style=\tf]
\define[1]\Action{{\se #1}}

\useURL[author-email][mailto:joe.schafer@delta46.us][][joe.schafer@delta46.us]
\useURL[author-linkedin][http://linkedin.com/in/jschaf][][linkedin.com/in/jschaf]
\useURL[author-github][http://github.com/jschaf][][github.com/jschaf]
\useURL[author-blog][http://blog.d46.us][][blog.d46.us]
\useURL[eslint-closure][https://github.com/google/eslint-closure][][library]

\useURL[esup][https://github.com/jschaf/esup][][Emacs Startup Profiler]
\useURL[pylint][https://github.com/jschaf/pylint-flask][][Python Plugin for Flask]
\useURL[pylint-debian][https://packages.debian.org/sid/main/python3-pylint-flask][][Debian]
\useURL[pylint-downloads][http://pypi-ranking.info/module/pylint-flask][][10,000]

\showgrid
% \showframe

% Begin Document
\starttext

\startGoldenColumns
\Name{Joe Schafer}
\GoldenColumns
\startbaselinecorrection
\setupinterlinespace[line=\SmallBaseline]
\Contact{\from[author-email]}
\Contact{\from[author-linkedin]}
\Contact{\from[author-github]}
\Contact{\from[author-blog]}
\stopbaselinecorrection
\stopGoldenColumns


\startGoldenColumns

\Heading{Work Experience}

\WorkHeading{Google}{Software Engineer}{2016-present}
\startitemize
\item \Action{Released} an open source \from[eslint-closure] to check the style
  of Google Closure JavaScript code.
\item \Action{Split} a 4{\sc gb} monolithic binary into 3 microservices.
\item \Action{Developed} a project management application that integrates with Gmail
  through JavaScript, Python and Java.
\item \Action{Reduced} application testing time 20-fold by implementing hot-reload of JavaScript.
\stopitemize

\WorkHeading{U.S. Army}{Infantry Instructor}{2014-16}
\startitemize
\item \Action{Influenced} 5 levels of executives to transition the Infantry
  training course to a committee design resulting in every subsequent class
  achieving record high performance.
\item \Action{Taught} and \Action{mentored} 120 Infantry lieutenants to lead a
  platoon in battle and plan decisive operations.
\stopitemize

\WorkHeading{U.S. Army}{Infantry Officer}{2010-14}
\startitemize
\item \Action{Planned} all logistics operations for an 815-man Airborne Infantry
  Battalion capable of worldwide deployment in 96 hours.
\item \Action{Planned} and \Action{led} 25 combat missions in Afghanistan
  through 6 enemy ambushes and Improvised Explosive Device (IED) attacks.
\stopitemize

\Heading{Education}

\EducationHeading{Stanford, Graduate School of Business}{2017}
Certificate in innovation and entrepreneurship.\par
Fulltime, on campus, one month, intensive program.

\blank

\EducationHeading{United States Military Academy, West Point}{2010}
B.S., Computer Science.

\GoldenColumns
\blank
\Heading{Open Source Projects}

\OpenSourceProject{\from[esup]}{
  Profiles the start-up time of a popular programming editor.  Over 110 stars on
  GitHub and 5,000 downloads.
}

\blank[0.43\Baseline]
\OpenSourceProject{\from[pylint]}{
  A plugin for Pylint, a static analysis tool, to integrate with the web
  framework Flask.  Packaged by \from[pylint-debian].  Over
  \from[pylint-downloads] downloads.
}

\Heading{Languages}
\LanguageProficiency{Proficient}{Java, JavaScript, Python, {\sc SQL}, Bash, Lisp}
\LanguageProficiency{Familiar}{Rust, Go, TypeScript, Ada}

\blank[1*line]
\Heading{Hobbies}
\Hobby{Powerlifting. deadlift: 425lb, squat: 375lb, bench: 260lb}
\Hobby{Exploring new programming languages like Rust, Dart, and TypeScript.}

\stopGoldenColumns

\stoptext