% Warn when deprecated LaTeX commands are used
\RequirePackage[l2tabu, orthodox]{nag}

\documentclass[letterpaper]{jschaf-resume}

% Make nice clickable urls
\usepackage[pdftex, pdfusetitle,colorlinks=false,pdfborder={0 0 0}]{hyperref}

% Use expanded computer modern that has bold small caps
\usepackage[T1]{fontenc}
\usepackage{array}

\usepackage[absolute]{textpos}
\usepackage{tabularx}
\usepackage{array}
\usepackage{baselinegrid}
\usepackage{tocloft}



\usepackage{calc}

% \usepackage{microtype}

% more control over enumerate
\usepackage{enumitem}

% Superscripts, 1st, 2nd, etc...
\newcommand{\st}{\textsuperscript{st}}
\newcommand{\nd}{\textsuperscript{nd}}
\newcommand{\rd}{\textsuperscript{rd}}
\newcommand{\thh}{\textsuperscript{th}}

% Setup list style
% TODO: Spacing
\renewcommand{\theenumi}{\arabic{enumi}}
\renewcommand{\labelenumi}{\theenumi.}

\renewcommand{\theenumii}{\alph{enumii}}
\renewcommand{\labelenumii}{\theenumii.}

\renewcommand{\theenumiii}{\arabic{enumiii}}
\renewcommand{\labelenumiii}{(\theenumiii)}

\renewcommand{\theenumiv}{\alph{enumiv}}
\renewcommand{\labelenumiv}{(\theenumiv)}

\title{Joe Schafer Resume}
\author{Joe Schafer}
\date{\today}

\hypersetup{%
pdftitle={Joe Schafer Resume},%
pdfauthor={Joe Schafer},%
pdfkeywords={Resume,Google,U.S. Army},%
}%
\newcommand{\Mark}[1]{\textsuperscript{#1}}

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\cventry}[3]{
\begin{tabularx}{3.5in}{X<{\cftdotfill{\cftsecdotsep}}@{}r}
  \textbf{#1} #2 & #3 \\
\end{tabularx}}

\begin{document}
% \lastupdated
% \twocolumn[{%
%  \centering
%  \LARGE The Title \\[1.5em]
%  \large First Author\Mark{1},
%         Second Author\Mark{2},
%         Third Author\Mark{1},
%         Fourth Author\Mark{2}
%     and Fifth Author\Mark{3}\\[1em]
%  \normalsize
%  \begin{tabular}{*{2}{>{\centering}p{.25\textwidth}}}
%   \Mark{1}Department1 & \Mark{2}Department2 \tabularnewline
%   School1 & School2  \tabularnewline
%   \url{email1} & \url{email2}
%  \end{tabular}\\[3em] % some more space after the title part
% }]

\section{Work}

\cventry{Google}{Software Engineer}{2016-present}
\begin{itemize}
  \resitem Developed a project management application that integrates with Gmail
  through JavaScript, Python and Java.  Increased development velocity by
  reducing application testing time by 20x.
\end{itemize}

\cventry{U.S. Army}{Infantry Instructor}{2014-16}
\begin{itemize}
  \resitem Taught and mentored 120 Infantry lieutenants to lead a platoon in
  battle, plan decisive operations, and overcome the adversity of combat.
  Influenced 5 levels of senior executives to transition school from a
  hierarchical organizational structure to committee design resulting in every
  subsequent class achieving record high performance.
\end{itemize}

\cventry{U.S. Army}{Infantry Officer}{2010-14}

\begin{itemize}
  \resitem Planned all logistics operations for an 815-man Airborne Infantry
  Battalion capable of worldwide deployment in 96 hours.  Planned and moved 100
  vehicles and 30 containers over 1000 miles on time and on schedule.  Ranked
  \#1 of 6 peer leaders for leadership and influence two levels up.  Led a
  22-man, heavy weapons platoon with \$17.5M of equipment through combat
  operations in Afghanistan.  Planned and led 25 tactical ground missions over
  3,000 miles in combat.  Led through six Improvised Explosive Device (IED)
  attacks and five enemy ambushes.
\end{itemize}

\section{Education}

Pellentesque dapibus suscipit ligula.  Donec posuere augue in quam.  Etiam vel
tortor sodales tellus ultricies commodo.  Suspendisse potenti.  Aenean in sem ac
leo mollis blandit.  Donec neque quam, dignissim in, mollis nec, sagittis eu,
wisi.  Phasellus lacus.  Etiam laoreet quam sed arcu.  Phasellus at dui in
ligula mollis ultricies.  Integer placerat tristique nisl.  Praesent augue.
Fusce commodo.  Vestibulum convallis, lorem a tempus semper, dui dui euismod
elit, vitae placerat urna tortor vitae lacus.  Nullam libero mauris, consequat
quis, varius et, dictum id, arcu.  Mauris mollis tincidunt felis.  Aliquam
feugiat tellus ut neque.  Nulla facilisis, risus a rhoncus fermentum, tellus
tellus lacinia purus, et dictum nunc justo sit amet elit.

\section{Open Source Software}

Phasellus lacus. Pellentesque dapibus suscipit ligula.  Phasellus at dui in
ligula mollis ultricies.

Aliquam posuere. Nunc rutrum turpis sed pede.  Aliquam posuere.


\showbaselinegrid
\end{document}