% Page Layout
\setuppapersize[letter]
\setuplayout[grid=yes,width=6.5in,header=0pt]

% Baseline Grid
% default line=2.8ex
\newdimen\Baseline
\Baseline=14pt
\newdimen\SmallBaseline
\SmallBaseline=0.806\Baseline
\setupinterlinespace[line=\Baseline]

% Fonts
\definefontfeature[default][default]
                  [protrusion=quality, expansion=quality, onum=yes]
\definefontsize[e]
\definebodyfontenvironment[default][e=3]

\setupalign[hz,hanging]
\definefontalternative[se]
\definefontalternative[liit]
\definefontalternative[li]
\definefontalternative[me]
\definefontalternative[meit]
\definefontalternative[seit]
\definefontalternative[bl]
\definefontalternative[blit]

\usetypescript[type-adobe]
\usetypescript[type-minionpro]
\usetypescript[type-myriadpro]
\starttypescript [myfont]
   \definetypeface [myfont] [rm] [serif] [minionpro] [regular]
   \definetypeface [myfont] [ss] [sans]  [myriadpro] [regular]
   \definetypeface [myfont] [tt] [mono]  [cursor]    [default] [rscale=1.163]
   \definetypeface [myfont] [mm] [math]  [palatino]  [default] [rscale=1.050]
\stoptypescript
\setupbodyfont[myfont,11pt]

\definebar[LightUnderline][rulethickness=0.1,offset=-0.2,continue=yes]

\starttexdefinition unexpanded StyleUrl #1
   \startbar[LightUnderline]
     \from[#1]
   \stopbar
\stoptexdefinition

% Hyphenation
\hyphenation{Goo-gle Type-Script Git-Hub}

% Columns
\define\GoldenRatio{0.61996}
\newdimen\ColumnGutter
\ColumnGutter=1cm
\defineparagraphs[GoldenColumns][n=2]
\setupparagraphs[GoldenColumns][1][width=\dimexpr\GoldenRatio\textwidth - 0.5\ColumnGutter\relax]
\setupparagraphs[GoldenColumns][2][distance=\ColumnGutter]

% Content
\define[1]\Name{\blank[12pt]{\tfe #1}}
\define[1]\Heading{
  \color[HeadingColor]{\ssa #1}
  \blank[halfline]}
\define\CompanyLength{2.7cm}
\define[3]\WorkHeading{
  {\tfa \dontleavehmode\hbox to \CompanyLength{#1\hfil} #2 \hfill #3}
  \vskip -0.5\baselineskip
}
\define[2]\EducationHeading{{\se #1}\hfill #2\par}

\define[2]\OpenSourceProject{
  {\tf #1}
  \startalignment[flushleft] #2 \stopalignment
  \blank[line]
}

\define[1]\Contact{{\tf #1\par}}
\define[2]\LanguageProficiency{
  \startalignment[flushleft] {\se #1}:  #2 \stopalignment
}
\define[1]\Hobby{
  \startalignment[flushleft] #1\stopalignment}

% Colors
\definecolor[HeadingColor][0.6(red,black)]
\definecolor[UrlColor][0.6(blue,black)]

\setupitemize[each][inmargin][symbol=nosymbol,inbetween={\blank[0.5\Baseline]}]
\setupinteraction[state=start,color=UrlColor,style=\tf]
\define[1]\Action{{\se #1}}

\useURL[author-email][mailto:joe.schafer@delta46.us][][joe.schafer@delta46.us]
\useURL[author-linkedin][http://linkedin.com/in/jschaf][][linkedin.com/in/jschaf]
\useURL[author-github][http://github.com/jschaf][][github.com/jschaf]
\useURL[author-blog][http://blog.d46.us][][blog.d46.us]
\useURL[eslint-closure][https://github.com/google/eslint-closure][][ESLint for Google Closure JS]
\useURL[eslint-closure-library][https://github.com/google/eslint-closure][][library]
\useURL[esup][https://github.com/jschaf/esup][][Emacs Startup Profiler]
\useURL[pylint][https://github.com/jschaf/pylint-flask][][Python Plugin for Flask]
\useURL[pylint-debian][https://packages.debian.org/sid/main/python3-pylint-flask][][Debian]
\useURL[pylint-downloads][http://pypi-ranking.info/module/pylint-flask][][10,000]

% \showgrid
% \showframe

% Begin Document
\starttext
\startGoldenColumns
\vskip 0.55\Baseline
\Name{Joe Schafer}
\GoldenColumns
\Contact{San Francisco Bay Area}
\Contact{\from[author-email]}
\Contact{\from[author-linkedin]}
\Contact{\from[author-github]}
\Contact{\from[author-blog]}
\stopGoldenColumns


\startGoldenColumns

\Heading{Work Experience}

\WorkHeading{Google}{Software Engineer}{2016-present}
\startitemize
\item \Action{Released} an open source \from[eslint-closure-library] to check the style
  of Google Closure JavaScript code.
\item \Action{Split} a 4GB monolithic binary into 3 microservices.
\item \Action{Developed} a project management application that integrates with Gmail
  through JavaScript, Python and Java.
\item \Action{Reduced} application testing time 20-fold by implementing hot-reload of JavaScript.
\stopitemize

\WorkHeading{U.S. Army}{Infantry Instructor}{2014-16}
\startitemize
\item \Action{Influenced} 5 levels of executives to transition the Infantry
  training course to a committee design resulting in every subsequent class
  achieving record high performance.
\item \Action{Taught} and \Action{mentored} 120 Infantry lieutenants to lead a
  platoon in battle and plan decisive operations.
\stopitemize

\WorkHeading{U.S. Army}{Infantry Officer}{2010-14}
\startitemize
\item \Action{Rated} \#1 of 5 peers. Chosen to plan all logistics operations for an 815-man Airborne Infantry Battalion.
\item \Action{Planned} and \Action{led} 25 combat missions in Afghanistan
  through 6 enemy ambushes and Improvised Explosive Device (IED) attacks.
\stopitemize

\vskip \Baseline
\Heading{Education}

\EducationHeading{Stanford, Graduate School of Business}{2017}
Certificate in innovation and entrepreneurship.\par
Fulltime, on campus, one month, intensive program.

\blank

\EducationHeading{United States Military Academy, West Point}{2010}
B.S., Computer Science.

\GoldenColumns
\blank
\Heading{Open Source Projects}

\vskip 0.5\baselineskip
\OpenSourceProject{\StyleUrl{eslint-closure}}{
  A heavily customized ESLint configuration and plugin for JavaScript following
  the Google style guide.
}

\OpenSourceProject{\StyleUrl{esup}}{
  Profiles the start-up time of a popular programming editor.  Over 110 stars on
  GitHub and 5,000 downloads.
}

\OpenSourceProject{\StyleUrl{pylint}}{
  A plugin for Pylint, a static analysis tool, to integrate with the web
  framework Flask.  Packaged by \StyleUrl{pylint-debian}.  Over
  \StyleUrl{pylint-downloads} downloads.
}

\vskip 0.5\Baseline
\Heading{Languages}
\LanguageProficiency{Proficient}{Java, JavaScript, Python, {\sc SQL}, Bash, Emacs Lisp, \LaTeX}
\LanguageProficiency{Familiar}{Rust, Go, TypeScript, Ada}

\vskip 1.5\Baseline
\Heading{Hobbies}
\Hobby{Powerlifting}
\blank[line]
\Hobby{Exploring new programming languages like Rust, Dart, and TypeScript.}

\stopGoldenColumns